### 2018-04-11 paper/appendix.tex

% CDD systems:
$\expand{\mathcal{R}}$ always returns a CDD expansion of its input
(see \autoref{app:corr}, \autoref{lem:expand-corr}) that is minimal.
% discussion: there are variations:
$\expand{ \mathcal{R} }$ is certainly not unique as an algorithm for
generating a minimal CDD expansion.
%
In particular, feasible variations of $\expand{ \mathcal{R} }$ can be
generated from different implementations of $\sharingclause$, each of
which chooses clause-relations pairs to return based on different
heuristics.
%
We expect that other expansion algorithms can also be developed by
generalizing algorithms introduced in previous work on generating
compact verification conditions of hierarchical
programs~\cite{lal-qadeer15}.

@@

  % contains linear systems:
  For goal \textbf{(1)}, let $\mathcal{S}$ be an arbitrary linear
  system.
  %
  $\mathcal{S}$ is CDD if for each clause $\mathcal{C}$ in
  $\mathcal{S}$, for each pair of distinct relational predicates in
  the body of $\mathcal{C}$, the transitive dependence are disjoint
  (\autoref{defn:cdds}).
  %
  Let $\mathcal{C}$ be an arbitrary clause in $\mathcal{S}$.
  %
  $\mathcal{C}$ has no pairs of distinct clauses, by the fact that
  $\mathcal{S}$ is linear.
  %
  Therefore, $\mathcal{S}$ is CDD.

  % contains body-disjoint systems:
  For goal \textbf{(2)}, let $\mathcal{S}$ be an arbitrary
  body-disjoint system.
  %
  The dependence relation of $\mathcal{S}$ is a tree $T$, by the
  definition of a body-disjoint system.
  %
  Let $\mathcal{C}$ be an arbitrary clause in $\mathcal{S}$, with
  distinct relational predicates $R_0$ and $R_1$ in its body.
  %
  All dependences of $R_0$ and $R_1$ are in subtrees of $T$, which
  are disjoint by the definition of a tree.
  %
  Thus, $\mathcal{S}$ is CDD, by \autoref{defn:cdds}.

@@

\section{Proof of Correctness}
\label{app:corr}
%
In this section, we give a proof that \sys is a correct solver for
recursion-free CHC systems.
%
We first establish lemmas for the correctness of each procedure used
by \sys, namely \textsc{Collapse} (\autoref{lem:expansion-sound} and
\autoref{lem:expansion-complete}), $\expand{\mathcal{R}}$
(\autoref{lem:expand-corr}), and $\solvecdd{ \mathcal{R} }$
(\autoref{lem:vc}, \autoref{lem:cdd-soln-sound}, and
\autoref{lem:cdd-soln-complete}).
%
We combine the lemmas to prove correctness of \sys
(\autoref{thm:corr}).

% lem: result connecting expansions to constructing solutions
For CHC systems $\mathcal{S}$ and $\mathcal{S}'$, if $\mathcal{S}'$ is
an expansion of $\mathcal{S}$, then the result of collapsing a
solution of $\mathcal{S}'$ is a solution of $\mathcal{S}$.
%
\begin{lem}
  \label{lem:expansion-sound}
  For $\mathcal{R}, \mathcal{R}' \in \relpreds$, $\mathcal{S} \in
  \chcs{ \mathcal{R} }$, $\mathcal{S}' \in \chcs{ \mathcal{R}' }$,
  $\sigma' \in \interps{ \mathcal{R}' }$, and $\eta : \mathcal{R}' \to
  \mathcal{R}$ a correspondence from $\mathcal{S}'$ to $\mathcal{S}$,
  $\collapse{\eta}{\sigma'}$ is a solution of $\mathcal{S}$.
\end{lem}
%
\begin{proof}
  % introduce 
  Let $\mathcal{B} \in \bodies{\mathcal{R}}$, $\varphi \in \formulas$,
  and $R \in \mathcal{R}$ be such that $((\mathcal{B}, \varphi),
  R(\vars{ \mathcal{S} }(R))) \in \mathcal{S}$.
  %
  For each $R' \in \mathcal{R}'$ such that $\eta(R') = R$, there is
  some $\mathcal{B}' \in \bodies{ \mathcal{R}' }$ such that
  $((\mathcal{B}', \varphi), R'(\vars{ \mathcal{S} }(R))) \in
  \mathcal{S}'$, by the fact that $\mathcal{S}'$ is an expansion of
  $\mathcal{S}$ and the definition of an expansion.
  %
  $\sigma'(\mathcal{B}'), \varphi \entails \sigma'(\mathcal{R}')$ by
  the fact that $\sigma'$ is a solution of $\mathcal{S}'$.
  %
  $\collapse{ \eta }{ \sigma' }(\mathcal{B}), \varphi \entails
  \sigma'(\mathcal{R}')$, by the definition of
  $\collapse{\eta}{\sigma'}$.
  %
  Therefore,
  %
  \[ \collapse{ \eta }{ \sigma' }( \mathcal{B} ), \varphi \entails %
  \left( \bigland_{ \substack{R' \in \mathcal{R}' \\ \eta(R') = R} }
  \sigma(R') \right) = %
  \collapse{\eta}{\sigma'}(\mathcal{R}') 
  \]
  % 
  Therefore, $\collapse{\eta}{\sigma'}$ is a solution of clause
  $((\mathcal{B}, \varphi), R(\varsof{ \mathcal{S} }(R)))$.
  %
  Therefore, $\collapse{\eta}{\sigma'}$ is a solution of
  $\mathcal{S}$.
\end{proof}

% completeness of expansions:
For CHC solvable system $\mathcal{S}$, each expansion of $\mathcal{S}$
is solvable.
\begin{lem}
  \label{lem:expansion-complete}
  For $\mathcal{R}, \mathcal{R}' \in \relpreds$, $\mathcal{S} \in
  \chcs{ \mathcal{R} }$ such that $\mathcal{S}$ is solvable, and
  $\mathcal{S}' \in \chcs{ \mathcal{R}' }$ such that $\mathcal{S'}$ is
  an expansion of $\mathcal{S}$, $\mathcal{S}'$ is solvable.
\end{lem}
%
\begin{proof}
  Let $\sigma : \mathcal{R} \to \formulas$ be a solution of
  $\mathcal{S}$, and let $\eta : \mathcal{R}' \to \mathcal{R}$ be a
  correspondence from $\mathcal{R}'$ to $\mathcal{R}$.
  %
  Let $\sigma' : \mathcal{R}' \to \formulas$ be such that for each $R'
  \in \mathcal{R}'$, $\sigma'(R') = \sigma(\eta(R'))$.
  %
  Then $\sigma$ is a solution of $\mathcal{S}'$.
\end{proof}

% CDD systems:
$\expand{\mathcal{R}}$ always returns a CDD expansion of its input.
%
\begin{lem}
  \label{lem:expand-corr}
  For $\mathcal{R} \in \relpreds$ and $\mathcal{S} \in \chcs{
    \mathcal{R} }$, $\mathcal{S} \in \chcs{ \ctxs{ \mathcal{R} } }$,
  and $\eta : \ctxs{ \mathcal{R} } \to \mathcal{R}$ such that
  $(\mathcal{S}', \eta) = \expand{\mathcal{R}}(\mathcal{S})$, $\eta$
  is a correspondence from $\mathcal{S}'$ to $\mathcal{S}$.
\end{lem}
%
\begin{proof}
  Proof by induction on the evaluation of $\expand{ \mathcal{R} }$ on
  an arbitrary $\mathcal{S} \in \chcs{ \mathcal{R} }$.
  % inductive fact:
  The inductive fact is that in each step of evaluation \expandaux,
  $\corr{ \mathcal{R} }$ is a correspondence from argument
  $\mathcal{S}'$ to $\mathcal{S}$.
  % base case:
  For the base case, \expandaux is called initially on $\mathcal{S}$,
  by \autoref{alg:expand}.
  % 
  $\corr{ \mathcal{R} }$ is a correspondence from $\mathcal{S}$ to
  itself, by the definition of $\corr{ \mathcal{R} }$
  (\autoref{app:cons-cdd}).

  % inductive case:
  For the inductive case, for $\mathcal{C} \in \mathcal{S}$ and $R \in
  \ctxs{ \mathcal{R} }$, $\expandaux$ calls itself on $\copyrel{
    \mathcal{R} }(\mathcal{S}, \mathcal{C}, R)$.
  %
  For each $\mathcal{S}' \in \chcs{ \ctxs{ \mathcal{R} } }$ such that
  $\corr{ \mathcal{R} }$ is a correspondence from $\mathcal{S}'$ to
  $\mathcal{S}$, $\corr{ \mathcal{R} }$ is a correspondence from
  $\copyrel{ \mathcal{R} }( \mathcal{S}', \mathcal{C}, R)$ to
  $\mathcal{S}$, by definition of $\copyrel{ \mathcal{R} }$
  (\autoref{app:cons-cdd}).
  %
  By this fact and the inductive hypothesis, $\corr{ \mathcal{R}}$ is
  a correspondence from $\copyrel{ \mathcal{R} }( \mathcal{S}',
  \mathcal{C}, R)$ to $\mathcal{S}$.

  % final claim: expand returns an expansion:
  $\expandaux{ \mathcal{R} }$ returns its parameter at some step, by
  \autoref{alg:expand}.
  %
  Therefore, $\expandaux$ returns an expansion of $\mathcal{S}$.

  % prove that returned system is CDD:
  For $\mathcal{S}' \in \chcs{ \ctxs{ \mathcal{R} } }$ and $\eta :
  \ctxs{\mathcal{R}} \to \mathcal{R}$, if $(\mathcal{S}', \eta) =
  \expand{ \mathcal{R} }( \mathcal{S} )$, then $\sharingclause(
  \mathcal{S}') = \none$, by the definition of $\expand{ \mathcal{R}
  }$.
  %
  If $\sharingclause(\mathcal{S}') = \none$, then $\mathcal{S}'$ is
  CDD, by the definition of $\sharingclause$ and CDD systems
  (\autoref{defn:cdds}).
  %
  Therefore, $\mathcal{S}'$ is CDD.
\end{proof}
%
Furthermore, $\expand{ \mathcal{R} }$ returns a \emph{minimal} CDD
expansion of its input.
%
This fact is not required to prove \autoref{thm:corr}, and thus a
complete proof is withheld.

% lem: VC's characterize system sat:
For each CHC system $\mathcal{S}$, $\mathcal{S}$ has a solution if and
only if the verification condition of $\mathcal{S}$ is unsatisfiable.
%
\begin{lem}
  \label{lem:vc}
  For $\mathcal{R} \in \relpreds$ and $\mathcal{S} \in \chcs{
    \mathcal{R} }$ that is CDD and solvable, $\vc{ \mathcal{R} }(
  \mathcal{S} )$ is unsatisfiable.
\end{lem}
%
\begin{proof}
  %
  Assume that $\mathcal{S}$ has solution $\sigma$ and $m$ is a model
  of $\vc{ \mathcal{R} }( \mathcal{S})$.
  %
  There are some relational predicates $\mathcal{R}' \subseteq
  \mathcal{R}$ containing $\queryof{ \mathcal{S} }$ such that for each
  $R' \in \mathcal{R}'$, $m(\used{R})$ holds, by the definition of
  $\vc{ \mathcal{R} }$ (\autoref{sec:solve-cdd}).
  %
  For each $R'$, the interpretation of $m$ over $\varsof{ \mathcal{R}'
  }$ must satisfy $\sigma(R')$, by well-founded induction on $\deps_S$
  restricted to $\mathcal{R}'$.
  %
  But $\sigma(\queryof{ \mathcal{S} }) = \false$, by the definition of
  a solution of a CHC system (\autoref{defn:chc-soln}).
  %
  Therefore, there can be no such model $m$.
  %
  Therefore, $\vc{ \mathcal{R} }( \mathcal{S} )$ is unsatisfiable.
\end{proof}

\begin{lem}
  \label{lem:solve-aux}
  For $\mathcal{R} \in \relpreds$ and $\mathcal{S} \in \chcs{
    \mathcal{R} }$ such that $\vc{ \mathcal{R} }(\mathcal{S})$ is
  unsatisfiable, $\solvecdd{ \mathcal{R} }(\mathcal{S})$ is a solution
  of $\mathcal{S}$.
\end{lem}
%
\begin{proof}
  % overview of structure:
  Proof by induction on the evaluation of $\solveaux$ on
  interpretation $\sigma$.
  %
  The inductive fact is that at each step of evaluation, $\sigma$ is a
  partial solution of $\mathcal{S}$ such that $\sigma(\mathcal{S})$
  % base case:
  For the base case, \solveaux is initially called on the empty
  interpretation.
  %
  Therefore, $\vc{\mathcal{R}}(\sigma(\mathcal{S})) = \vc{
    \mathcal{R}}(\mathcal{S})$, which is unsatisfiable.

  % inductive case:
  For the inductive case, in each step, \solveaux calls itself on an
  interpretation $\sigma'$, which is its argument $\sigma$, extended
  to map relational predicate $R$ to an interpolant of $\prectr{
    \mathcal{R} }( \mathcal{S}, \sigma, R)$ and $\postctr{ \mathcal{R}
  }( \mathcal{S}, \sigma, R)$.
  %
  $\sigma'$ is a partial solution of $\mathcal{S}$ by a combination of
  the inductive hypothesis that $\sigma$ is a partial solution, the
  fact that any extension of $\sigma$ that maps $R$ to a formula
  implied by $\prectr{ \mathcal{R} }( \mathcal{S}, \sigma, R)$ is a
  partial solution, and the definition of an interpolant
  (\autoref{defn:itps}).
  %
  $\vc{ \mathcal{R} }(\sigma'(\mathcal{S}))$ is unsatisfiable by a
  combination of the inductive hypothesis that $\vc{ \mathcal{R}
  }(\sigma(\mathcal{ S }))$ is unsatisfiable, that for any extension
  $\sigma''$ of $\sigma$ that maps $R$ to a formula inconsistent with
  $\postctr{ \mathcal{R} }( \mathcal{S}, \sigma, R)$, $\vc{
    \mathcal{R} }(\sigma''(\mathcal{S}))$ is unsatisfiable, and the
  definition of an interpolant (\autoref{defn:itps}).

  % prove goal:
  $\mathcal{R}'$ (defined at \autoref{alg:solve-cdd},
  \autoref{line:cons-nodeps}) is empty only if $\mathcal{R} \setminus
  \domainof{ \sigma }$ is empty, by induction on evaluation of
  \solveaux.
  %
  Therefore, \solveaux only returns its parameter $\sigma$ if $\sigma$
  is in fact a complete interpretation.
  %
  This fact, combined with the inductive fact, imply that \solveaux
  returns a solution of $\mathcal{S}$.
\end{proof}

% SolveCDD: establish soundness
For $\mathcal{R} \in \relpreds$, $\solvecdd{ \mathcal{R} }$ is a
correct CHC solver for CDD systems over $\mathcal{R}$.
%
\begin{lem}
  \label{lem:cdd-soln-sound}
  For $\mathcal{R} \in \relpreds$, %
  $\mathcal{S} \in \chcs{ \mathcal{R} }$ such that $\mathcal{S}$ is
  CDD, and %
  $\sigma \in \interps{ \mathcal{R} }$ such that %
  $\sigma = \solvecdd{ \mathcal{R} }(\mathcal{S})$, %
  $\sigma$ is a solution of $\mathcal{S}$.
\end{lem}
%
\begin{proof}
  %
  $\vc{ \mathcal{R} }(\mathcal{S})$ is unsatisfiable, by the fact that
  $\sigma \in \interps{ \mathcal{R} }$ \autoref{alg:solve-cdd},
  \autoref{line:check-sat}.
  %
  Therefore, $\solvecdd{ \mathcal{R} }(\mathcal{S})$ is the result of
  calling \solveaux, by \autoref{alg:solve-cdd},
  \autoref{line:check-sat}.
  %
  Therefore, \autoref{lem:solve-aux} and the fact that $\vc{
    \mathcal{R} }(\mathcal{S})$ is unsatisfiable imply that \solveaux
  returns a complete solution of $\mathcal{S}$.
\end{proof}

% SolveCDD: establish completeness
\begin{lem}
  \label{lem:cdd-soln-complete}
  For $\mathcal{R} \in \relpreds$ and %
  $\mathcal{S} \in \chcs{ \mathcal{R} }$ such that $\mathcal{S}$ is
  solvable and CDD, %
  there is some $\sigma \in \interps{ \mathcal{R} }$ such that %
  $\sigma = \solvecdd{ \mathcal{R} }(\mathcal{S})$.
\end{lem}
%
\begin{proof}
  % final claim:
  $\vc{ \mathcal{R} }(\mathcal{S})$ is not satisfiable, by
  \autoref{lem:vc} and the fact that $\mathcal{S}$ is solvable.
  %
  Therefore, $\solvecdd{ \mathcal{R} }$ is the result of running
  \solveaux, by \autoref{alg:solve-cdd}.
  %
  Therefore, by \autoref{lem:solve-aux} and the fact that
  $\mathcal{S}$ is solvable, $\solvecdd{ \mathcal{R} }$ returns a
  solution of $\mathcal{S}$.
\end{proof}

% proof of main theorem:
The following is a proof of correctness of \sys
(\autoref{sec:approach}, \autoref{thm:corr}).
%
\begin{proof}
  % if returns a map, then S is a solution
  Assume that for $\sigma \in \interps{ \mathcal{R} }$, $\sigma =
  \shara{ \mathcal{R} }( \mathcal{S} ) \in \interps{ \mathcal{R} }$.
  %
  Let $\mathcal{S'} \in \chcs{ \ctxs{ \mathcal{R} } }$ and $\eta :
  \ctxs{ \mathcal{R} } \to \mathcal{R}$ be such that $(\mathcal{S}',
  \eta) = \expand{ \mathcal{R} }( \mathcal{S} )$;
  %
  $\eta$ is a correspondence from $\mathcal{S'}$ to $\mathcal{S}$, by
  \autoref{lem:expand-corr}.
  %
  There is some $\sigma' \in \interps{ \mathcal{R}' }$ such that
  $\sigma' = \solvecdd{ \ctxs{ \mathcal{R} } }( \mathcal{S}' )$, by
  the definition of $\shara{ \mathcal{R} }$.
  %
  $\sigma'$ is a solution of $\mathcal{S}'$, by
  \autoref{lem:cdd-soln-sound}.
  %
  $\collapse{ \eta }{ \sigma' }$ is a solution of $\mathcal{S}$, by
  \autoref{lem:expansion-sound}.

  % if S is solvable, then shara returns a solution
  Assume that $\mathcal{S}$ is solvable.
  %
  Let $\mathcal{S'} \in \chcs{ \ctxs{ \mathcal{R} } }$ and $\eta :
  \ctxs{ \mathcal{R} } \to \mathcal{R}$ be such that $(\mathcal{S}',
  \eta) = \expand{ \mathcal{R} }( \mathcal{S} )$.
  %
  $\mathcal{S}'$ is a CDD expansion of $\mathcal{S}$, by
  \autoref{lem:expand-corr}.
  %
  $\mathcal{S}'$ is solvable, by \autoref{lem:expansion-complete}.
  %
  $\solvecdd{ \ctxs{ \mathcal{R} } }( \mathcal{S'}) \in \interps{
    \mathcal{R'} } $, by \autoref{lem:cdd-soln-complete}.
  %
  $\shara{\mathcal{R}} \in \interps{ \mathcal{R} }$, by
  \autoref{alg:shara}.
\end{proof}

>>>>

% CDD systems:
$\expand$ always returns a CDD expansion of its input
(see \autoref{app:corr}, \autoref{lem:expand-corr}) that is minimal.
% discussion: there are variations:
$\expand$ is certainly not unique as an algorithm for
generating a minimal CDD expansion.
%
In particular, feasible variations of $\expand$ can be
generated from different implementations of $\sharingclause$, each of
which chooses clause-relations pairs to return based on different
heuristics.
%
We expect that other expansion algorithms can also be developed by
generalizing algorithms introduced in previous work on generating
compact verification conditions of hierarchical
programs~\cite{lal-qadeer15}.

@@

  % contains linear systems:
  For goal \textbf{(1)}, let $S$ be an arbitrary linear
  system.
  %
  $S$ is CDD if for each clause $C$ in
  $S$, each pair of distinct predicates in
  the body of $C$, the transitive dependence are disjoint, and
  no predicates shows more than once in the body of $C$.
  (\autoref{defn:cdds}).
  %
  Let $C$ be an arbitrary clause in $S$.
  %
  The body of $C$ has no pair of distinct predicates or a predicates shows more than once, by the fact that
  $S$ is linear.
  %
  Therefore, $S$ is CDD.

  % contains body-disjoint systems:
  For goal \textbf{(2)}, let $S$ be an arbitrary
  body-disjoint system.
  %
  The dependence relation of $S$ is a tree $T$, by the
  definition of a body-disjoint system.
  %
  Let $C$ be an arbitrary clause in $S$, with
  distinct relational predicates $R_0$ and $R_1$ in its body.
  %
  All dependences of $R_0$ and $R_1$ are in subtrees of $T$, which
  are disjoint by the definition of a tree.
  %
  Thus, $S$ is CDD, by \autoref{defn:cdds}.

@@

\section{Proof of Correctness}
\label{app:corr}
%
In this section, we give a proof that \sys is a correct solver for
recursion-free CHC systems.
%
We first establish lemmas for the correctness of each procedure used
by \sys, namely \textsc{Collapse} (\autoref{lem:expansion-sound} and
\autoref{lem:expansion-complete}), $\expand$
(\autoref{lem:expand-corr}), and $\solvecdd$
(\autoref{lem:vc}, \autoref{lem:cdd-soln-sound}, and
\autoref{lem:cdd-soln-complete}).
%
We combine the lemmas to prove correctness of \sys
(\autoref{thm:corr}).

% lem: result connecting expansions to constructing solutions
For recursion-free CHC systems $S$ and $S'$, if $S'$ is
an expansion of $S$, then the result of collapsing a
solution of $S'$ is a solution of $S$.
%
\begin{lem}
  \label{lem:expansion-sound}
  For recursion-free CHC system $S'$ and $S$,
  $\sigma'$ is a solution of $S'$, and $\eta : \predof{S}' \to
  \predof{S}$ a correspondence from $\predof{S}'$ to $\predof{S}$,
  $\collapse{\eta}{\sigma'}$ is a solution of $S$.
\end{lem}
%
\begin{proof}
  % introduce 
  Let $\mathcal{B} \in \bodies{\mathcal{R}}$, $\varphi \in \formulas$,
  and $R \in \mathcal{R}$ be such that $((\mathcal{B}, \varphi),
  R(\vars{ \mathcal{S} }(R))) \in \mathcal{S}$.
  %
  For each predicate $P' \in \predof{S}'$ such that $\eta(P') = P$, there is
  some clause $C' \in S'$ such that $P' \in \bodyof{C'}$ by the fact that $S'$ is an expansion of
  $S$ and the definition of an expansion.
  %
  Let preicate $Q' \in \predof{S}'$ such that $Q'$ is the head of clause $C'$.
  % 
  $\sigma'[P'] \land \consof{C'} \entails \sigma'[Q']$ by
  the fact that $\sigma'$ is a solution of $S'$.
  %
  Therefore,
  %
  \[ \collapse{ \eta }{ \sigma' }[P] \land \consof{C'} \entails %
  \left( \bigland_{ \substack{Q' \in \predof{S}' \\ \eta(Q') = Q} }
  \sigma(Q') = %
  \collapse{\eta}{\sigma'}[Q'] \right)
  \]
  % 
  Therefore, $\collapse{\eta}{\sigma'}$ is a solution of $P$.
  %
  Therefore, $\collapse{\eta}{\sigma'}$ is a solution of
  $S$.
\end{proof}

% completeness of expansions:
For a recursion-free CHC system $S$ is solvalbe, each expansion of $S$
is solvable.
\begin{lem}
  \label{lem:expansion-complete}
  For a recursion-free CHC system $S$ is solvable, and
  $S'$ is
  an expansion of $S$, $S'$ is solvable.
\end{lem}
%
\begin{proof}
  Let $\sigma : P \to \formulas$ be a solution of
  $S$, and let $\eta : \predof{S}' \to \predof{S}$ be a
  correspondence from $S'$ to $S$.
  %
  Let $\sigma' : \predof{S}' \to \formulas$ be such that for each $P'
  \in \predof{S}'$, $\sigma'(P') = \sigma(\eta(P'))$.
  %
  Then $\sigma'$ is a solution of $S'$.
\end{proof}

% CDD systems:
$\expand$ always returns a CDD expansion of its input.
%
\begin{lem}
  \label{lem:expand-corr}
  For a recursion-free CHC system $S$ and $S'$, and $\eta : \predof{S'} \to \predof{S}$ such that
  $(S', \eta) = \expand(S)$, $\eta$
  is a correspondence from $S'$ to $S$, $S'$ is an CDD system and an expansion
  of $S$.
\end{lem}
%
\begin{proof}
  Proof by induction on the evaluation of $\expand$ on
  an arbitrary recursion-free CHC system $S$.
  % inductive fact:
  The inductive fact is that in each step of evaluation \expandaux,
  $\corr$ is a correspondence from argument
  $S'$ to $S$.
  % base case:
  For the base case, \expandaux is called initially on $S$,
  by \autoref{alg:expand}.
  % 
  $\corr$ is a correspondence from $S$ to
  itself, by the definition of $\corr$
  (\autoref{app:cons-cdd}).

  % inductive case:
  For the inductive case, for $C \in S$ and $P \in \predof{S}$, $\expandaux$ calls itself on 
  $\copyrel(S, C, P)$.
  %
  For each recursion-free CHC system $S'$ that generated by $\copyrel(S, C, P)$,
  $\corr$ is a correspondence from $S'$ to
  $S$ by definition of $\copyrel$
  (\autoref{app:cons-cdd}).
  %
  By this fact and the inductive hypothesis, $\corr$ is
  a correspondence from $\copyrel(S',
  C, P)$ to $S$.

  % final claim: expand returns an expansion:
  $\expandaux$ returns its parameter at some step, by
  \autoref{alg:expand}.
  %
  Therefore, $\expandaux$ returns an expansion of $S$.

  % prove that returned system is CDD:
  For a given recursion-free CHC system $S'$, if $(S', \eta) =
  \expand(S')$, 
  then $\sharingclause(S') = \none$, by the definition of $\expand$.
  %
  If $\sharingclause(S') = \none$, then $S'$ is
  CDD, by the definition of $\sharingclause$ and CDD systems
  (\autoref{defn:cdds}).
  %
  Therefore, $S'$ is CDD.
\end{proof}
%
Furthermore, $\expand$ returns a \emph{minimal} CDD
expansion of its input.
%
This fact is not required to prove \autoref{thm:corr}, and thus a
complete proof is withheld.

% lem: VC's characterize system sat:
For each recursion-free CHC system $S$, $S$ has a solution if and
only if all interpolants queries return interpolants.
%
\begin{lem}
  \label{lem:vc}
  Given a recursion-free CHC system $S$ that is CDD and solvable, for all predicates $P \in \predof{S}$,
   $\solveitp(\prectr(\cc{P},\sigma),\postctr(\cc{P},\sigma))$ returns a interpolatn $I$.
\end{lem}
%
\begin{proof}
  %
  Assume that $S$ has solution $\sigma$ and there are
  some predicates $P \in \predof{S}$ such that $\solveitp(\prectr(\cc{P},\sigma'),\postctr(\cc{P},\sigma'))$
  returns $SAT$, which means there is a model $m$ for the conjuntion of $\prectr(\cc{P},\sigma')$
  and $\postctr(\cc{P},\sigma')$.
  %
  But $\postctr(\cc{P},\sigma) = \false$, by the definition of
  a solution of a CHC system.
  %
  Therefore, there can be no such model $m$.
  %
  Therefore, $\solveitp(\prectr(\cc{P},\sigma'),\postctr(\cc{P},\sigma'))$ always returns interpolant.
\end{proof}

\begin{lem}
  \label{lem:solve-aux}
  Given a recursion-free CHC system $S$ that is CDD, if for all predciates $P \in \predof{S}$, 
  $\solveitp(\prectr(\cc{P},\sigma),\postctr(\cc{P},\sigma))$ returns a interpolatn $I$, 
  then $\solvecdd(S)$ is a solution of $S$.
\end{lem}
%
\begin{proof}
  % overview of structure:
  Proof by induction on the $\solvecdd(S)$ calles $\solveitp$ on all predicates $P \in \predof{S}$
  in a topolgical order.
  %
  The inductive fact is that at each step of calling $\solveitp$, $\sigma$ is a
  partial solution of $S$.
  % base case:
  For the base case, $\predof{S} = \varnothing$,
  %
  Therefore, $\sigma$ is a solution of $S$.

  % inductive case:
  For the inductive case, in each step, $\solvecdd$ calls $\solveitp$ on
  a predicate $P \in \predof{S}$ with partial solution $\sigma$, which
  contains all solutions of predciates $P \in \depsof{S}$.
  %
  Based on the definition of an interpolant(\autoref{defn:itps}), $\sigma$
  is a partial solution of $S$, then $\prectr(\cc{P},\sigma')$ and $\postctr(\cc{P},\sigma))$
  are inconsistent.
  %
  The interpolant $I$ returns by $\solveitp(\prectr(\cc{P},\sigma),\postctr(\cc{P},\sigma))$ entails
  by all clause that head is $P$ and $\bodyof{P}$ is substituted by partial solution $\sigma$.
  %
  $I$ also is inconsistment with all constrains shows later that support the query clause.
  %
  Then $\solvecdd$ updates $\sigma$ by binding $P$ to $I$, which makes the new $\sigma$ also a partial
  solution of $S$.

  %
  Base case combined with the inductive case, imply that \solvecdd
  returns a solution of $S$.
\end{proof}

% SolveCDD: establish soundness
$\solvecdd$ is a
correct CHC solver for CDD systems $S$.
%
\begin{lem}
  \label{lem:cdd-soln-sound}
  For a given CDD system $S$, and $\sigma = \solvecdd(S)$, %
  $\sigma$ is a solution of $\mathcal{S}$.
\end{lem}
%
\begin{proof}
  %
  $\solvecdd{S}$ returns $\sigma$ implies that for all predicates 
  $P \in \predof{S}$, $\solveitp(\prectr(\cc{P},\sigma),\postctr(\cc{P},\sigma))$ returns a interpolatn $I$, 
  by the definition of $\solvecdd$ \autoref{alg:solve-cdd}. 
  %
  Therefore, \autoref{lem:solve-aux} implies that \solvecdd
  returns a complete solution of $S$.
\end{proof}

% SolveCDD: establish completeness
\begin{lem}
  \label{lem:cdd-soln-complete}
  For a CDD system $S$ such that $S$ is
  solvable, %
  there is some $\sigma$ such that %
  $\sigma = \solvecdd(S)$.
\end{lem}
%
\begin{proof}
  % final claim:
  for all predicates $P \in \predof{S}$, $\solveitp(\prectr(\cc{P},\sigma),\postctr(\cc{P},\sigma))$ returns a interpolatn $I$, by
  \autoref{lem:vc} and the fact that $\mathcal{S}$ is solvable.
  %
  Therefore, by \autoref{lem:solve-aux} and the fact that
  $S$ is solvable, $\solvecdd(S)$ returns a
  solution of $S$.
\end{proof}

% proof of main theorem:
The following is a proof of correctness of \sys
(\autoref{sec:approach}, \autoref{thm:corr}).
%
\begin{proof}
  Given recurion-free CHC systems $S$ and $S'$, and $\eta :\predof{S'} \to 
  \predof{S}$ such that $(S', \eta) = \expand(S)$, 
  then $S'$ is minimal CDD expansion of 
  $S$, and $\eta$ is a correspondence from $S'$ to $S$ by \autoref{lem:expand-corr}.
  %
  There is some $\sigma'$ such that
  $\sigma' = \solvecdd(S' )$, by
  the definition of $\shara$.
  %
  $\sigma'$ is a solution of $S'$, by
  \autoref{lem:cdd-soln-sound}.
  %
  $\collapse{ \eta }{ \sigma' }$ is a solution of $S$, by
  \autoref{lem:expansion-sound}.

  % if S is solvable, then shara returns a solution
  Assume that a recursion-free $S$ is solvable.
  %
  Let a recursion-free CHC system $S'$ and $\eta :
  \predof{S'} \to \predof{S}$ be such that $(S',
  \eta) = \expand(S)$.
  %
  $S'$ is a CDD expansion of $S$, by
  \autoref{lem:expand-corr}.
  %
  $S'$ is solvable, by \autoref{lem:expansion-complete}.
  %
  $\solvecdd(S')$ returns a solution $\sigma$ of $S'$ by \autoref{lem:cdd-soln-complete}.
  %
  $\shara$ returns a solution of $S$ by calling $\collapse{ \eta }{ \sigma' }$, based on
  \autoref{alg:shara}.
\end{proof}
